Architectures and Open pNets

### 2018-02-05 2018-Arch-pNets/arch-pNets.tex
Couple of minor edits

An architecture $A$ enforces coordination constraints on the
components in $\cB$.  The interface $(P_A, V_A)$ of an
architecture $A$ contains all ports of the coordinating
components $\cC$ and some additional ports, which must belong to
the components in $\cB$.  In the application $A(\cB)$, the ports
belonging to $P_A$ can only participate in the interactions
defined by the interaction model $\Gamma$ of $A$.  Ports which do
not belong to $P_A$ are not restricted and can participate in any
interaction.  In particular, they can join the interactions in
$\Gamma$ (see \eq{im:extension}).  If the interface of the
architecture covers all ports of the system, \ie $P = P_A$, we
have $P\setminus P_A = \emptyset$ and the only interactions
allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
that the restrictions imposed by \defn{archi:application} on the
set of operand components $\cB$ ensure that an interaction in
$\IMextend{\Gamma}{P}$ can only refer to variables of the
participating components.
%
Finally, the definition of $\IMextend{\Gamma}{P}$ requires that
an interaction from $\Gamma$ be involved in every interaction
belonging to $\IMextend{\Gamma}{P}$.  To allow the ports from $P
\setminus P_A$ to be fired independently in $A(\cB)$, one must
have $(\emptyset, \true, \noop) \in \Gamma$.

@@

\bibliographystyle{abbrv}
\bibliography{}

>>>>

An architecture $A$ enforces coordination constraints on the
components in $\cB$.  The interface $(P_A, V_A)$ of an
architecture $A$ contains all ports of the coordinating
components $\cC$ and some additional ports, which must belong to
the components in $\cB$.  In the application $A(\cB)$, the ports
belonging to $P_A$ can only participate in the interactions
defined by the interaction model $\Gamma$ of $A$.  Ports which do
not belong to $P_A$ are not restricted and can participate in any
interaction.  In particular, they can join the interactions in
$\Gamma$ (see \eq{im:extension}).  If the interface of the
architecture covers all ports of the system, \ie $P = P_A$, we
have $P\setminus P_A = \emptyset$ and the only interactions
allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
that the restrictions imposed by \defn{arch:application} on the
set of operand components $\cB$ ensure that an interaction in
$\IMextend{\Gamma}{P}$ can only refer to variables of the
participating components.
%
Finally, the definition of $\IMextend{\Gamma}{P}$ requires that
an interaction from $\Gamma$ be involved in every interaction
belonging to $\IMextend{\Gamma}{P}$.  To allow the ports from $P
\setminus P_A$ to be fired independently in $A(\cB)$, one must
have $(\emptyset, \true, \noop) \in \Gamma$.

@@

\bibliographystyle{abbrv}
\bibliography{biblio.bib}
